Applying Multi-Core Model Checking and Maximum Satisfiability to Hardware-Software Partitioning

### 2015-09-09 Docs/Paper/LaTex/template.tex
refactor main section

This article is organized as follows: Section~\ref{background} gives a background on optimization techniques, $\nu$Z, ESBMC, and OpenMP tools. 
Section~\ref{Mathematical-modeling} describes the informal and formal mathematical modeling. Section~\ref{ILPGA} briefly describes the ILP and GA algorithms, while Section~\ref{Analysis-of-the-partitioning-problem-using-vZ} presents the partitioning model using $\nu$Z. The SMT-based BMC method is presented in Section~\ref{Analysis-of-the-partitioning-problem-using-ESBMC}. In Section~\ref{Experimental-Evaluation}, we present the results of our experiments using several embedded systems applications. In Section~\ref{Related-Work}, we discuss the related work and we conclude and describe future work in Section~\ref{Conclusions}.

@@

%----------------------------------------------
\section{Partitioning problem using ILP-based,Genetic Algorithms}
\label{ILPGA}
%----------------------------------------------

The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2014}. Both use slack variables in order to be possible to represent constraints and to use commercial tools. However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout. The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.

%----------------------------------------------
\section{Analysis of the partitioning problem using $\nu$Z}
\label{Analysis-of-the-partitioning-problem-using-vZ}
%----------------------------------------------

@@

@@

\begin{table*}[t]
  \centering
  \caption{Experimental results of the complex benchmarks}  
  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}

@@

%vZ
\bottomrule[1.5pt]
\multirow{2}{*}{\textbf{vZ}}
&  T(s)   &  0.2   &  0.3   &  0.6   &  109   &  112    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  241    &  -   &  -  \\
\hline

@@

%ESBMC Parallel Binary
\multirow{2}{*}{\textbf{ESBMC-PB}}
&  T(s)   &  6   &  5   &  6   &  207   &  TO    &  MO   &  MO \\
&  Hp   &  15   &  47   &  38   &  241   &  -    &  -   &  -  \\
\bottomrule[1.5pt]
\end{tabular}
\label{Experimental-results-of-the-complex-benchmarks}
\end{table*}

>>>>

This article is organized as follows: Section~\ref{background} gives a background on optimization techniques, $\nu$Z, ESBMC, and OpenMP tools. 
Section~\ref{Mathematical-modeling} describes the informal and formal mathematical modeling. The SMT-based BMC method is presented in Section~\ref{Analysis-of-the-partitioning-problem-using-ESBMC}, and in particular, Section~\ref{Analysis-of-the-partitioning-problem-using-vZ} presents the partitioning model using $\nu$Z. In Section~\ref{Experimental-Evaluation}, we show the experimental results using several embedded systems applications. In Section~\ref{Related-Work}, we discuss the related work and we conclude and describe future work in Section~\ref{Conclusions}.

@@

\comment{
%----------------------------------------------
\section{Partitioning problem using ILP-based,Genetic Algorithms}
\label{ILPGA}
%----------------------------------------------

The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2014}. Both use slack variables in order to be possible to represent constraints and to use commercial tools. However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout. The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
}

@@

%----------------------------------------------
\subsection{Analysis of the partitioning problem using $\nu$Z (ESBMC-$\nu$Z)}
\label{Analysis-of-the-partitioning-problem-using-vZ}
%----------------------------------------------

@@

\begin{table*}[t]
  \centering
  \caption{Experimental results of the HW-SW partitioning benchmarks}  
  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}

@@

@@

%ESBMC Parallel Binary
\multirow{2}{*}{\textbf{ESBMC-PB}}
&  T(s)   &  6   &  5   &  6   &  207   &  TO    &  MO   &  MO \\
&  Hp   &  15   &  47   &  38   &  241   &  -    &  -   &  -  \\
\hline

%vZ
\multirow{2}{*}{\textbf{ESBMC-$\nu$Z}}
&  T(s)   &  0.2   &  0.3   &  0.6   &  109   &  112    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  241    &  -   &  -  \\

\bottomrule[1.5pt]
\end{tabular}
\label{Experimental-results-of-the-complex-benchmarks}
\end{table*}
